% include your own bib file like this:
%\bibliographystyle{acl}
%\bibliography{acl2014}

\newpage
\begin{thebibliography}{}

%\bibitem[\protect\citename{Aho and Ullman}1972]{Aho:72}
%Alfred~V. Aho and Jeffrey~D. Ullman.
%\newblock 1972.
%\newblock {\em The Theory of Parsing, Translation and Compiling}, volume~1.
%\newblock Prentice-{Hall}, Englewood Cliffs, NJ.
%
%\bibitem[\protect\citename{{American Psychological Association}}1983]{APA:83}
%{American Psychological Association}.
%\newblock 1983.
%\newblock {\em Publications Manual}.
%\newblock American Psychological Association, Washington, DC.
%
%\bibitem[\protect\citename{{Association for Computing Machinery}}1983]{ACM:83}
%{Association for Computing Machinery}.
%\newblock 1983.
%\newblock {\em Computing Reviews}, 24(11):503--512.
%
%\bibitem[\protect\citename{Chandra \bgroup et al.\egroup }1981]{Chandra:81}
%Ashok~K. Chandra, Dexter~C. Kozen, and Larry~J. Stockmeyer.
%\newblock 1981.
%\newblock Alternation.
%\newblock {\em Journal of the Association for Computing Machinery},
%  28(1):114--133.
%
%\bibitem[\protect\citename{Gusfield}1997]{Gusfield:97}
%Dan Gusfield.
%\newblock 1997.
%\newblock {\em Algorithms on Strings, Trees and Sequences}.
%\newblock Cambridge University Press, Cambridge, UK.


\bibitem[\protect\citename{Socher \bgroup et al.\egroup}2013]{Socher:2013},
Socher, Richard  and  Perelygin, Alex  and  Wu, Jean  and  Chuang, Jason  and  Manning, Christopher D.  and  Ng, Andrew Y.  and  Potts, Christopher. 
\newblock 2013. 
\newblock Recursive Deep Models for Semantic Compositionality Over a Sentiment Treebanka
\newblock {\em Proceedings of the 2013 Conference on {E}mpirical {M}ethods in {N}atural {L}anguage {P}rocessing} 

\bibitem[\protect\citename{Diakopoulos and Shamma} 2010]{Diakopoulos:2010},
N. Diakopoulos, D. A. Shamma. 
\newblock April, 2010.
\newblock Characterizing Debate Performance via Aggregated Twitter Sentiment.
\newblock {\em Conference on Human Factors in Computing Systems (CHI). }

\bibitem[\protect\citename{Agarwal \bgroup et al.\egroup}2011]{Agarwal:2011},
Apoorv Agarwal, Boyi Xie, Ilia Vovsha, Owen Rambow, and Rebecca Passonneau. 
\newblock 2011. 
\newblock Sentiment analysis of Twitter data. 
\newblock {\em In Proceedings of the Workshop on Languages in Social Media (LSM '11). Association for Computational Linguistics, Stroudsburg, PA, USA, 30-38.}

\bibitem[\protect\citename{Owoputi \bgroup et al.\egroup}2011]{Owoputi:2013},
Olutobi Owoputi and Chris Dyer and Kevin Gimpel and Nathan Schneider and Noah A. Smith. 
\newblock 2013. 
\newblock Improved part-of-speech tagging for online conversational text with word clusters
\newblock {\em In Proceedings of NAACL}

\bibitem[\protect\citename{Hu \bgroup et al.\egroup}2004]{Hu:2004},
Hu M, Liu B. 
\newblock 2004. 
\newblock Mining and summarizing customer reviews
\newblock {\em Proceedings of the tenth ACM SIGKDD international conference on Knowledge discovery and data mining. ACM, 2004: 168-177.}

\bibitem[\protect\citename{Go \bgroup et al.\egroup}2009]{Go:2009},
 Go A, Bhayani R, Huang L. 
\newblock 2009. 
\newblock Twitter sentiment classification using distant supervision
\newblock {\em CS224N Project Report, Stanford, 2009: 1-12.
}

\bibitem[\protect\citename{Mohammad \bgroup et al.\egroup}2013]{Mohammad:2013},
 Go A, Bhayani R, Huang L. 
\newblock 2013. 
\newblock NRC-Canada: Building the state-of-the-art in sentiment analysis of tweets
\newblock {\em arXiv preprint arXiv:1308.6242, 2013.
}

\bibitem[\protect\citename{Das and Chen}2001]{Das:2001},
Sanjiv Das and Mike Chen.
\newblock 2001. 
\newblock Yahoo! for Amazon: extracting market sentiment from stock message boards.
\newblock {\em In Proceedings of the 8th Asia Pacific Finance Association Annual Conference.
}

\bibitem[\protect\citename{Bo \bgroup et al.\egroup}2002]{Bo:2002},
Pang, Bo; Lillian Lee; and Shivakumar Vaithyanathan.
\newblock 2002. 
\newblock Thumbs up? sentiment classification using machine learning techniques. 
\newblock {\em In Proceedings of the Conference on Empirical Methods in Natural Language Processing. ACL.
}





\end{thebibliography}











